Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-02 manuscript.tex
small changes and comments up to section 3

\begin{enumerate}
\item Visualizing the partitions between clusters in combinations of features using tour methods, with both a grand tour and manual tour.
\item Interactively brushing groups of points to refine the cluster solution, like done with spin-and-brush tools.
\item Linking multiple displays to focus on particular clusters, and simplify the problem to better understand the clustering solution. 
\item Update displays based on user selections such as feature selection or cluster selection, or re-scaling.
\end{enumerate}

@@

The interface was implemented in \texttt{lionfish} and offers a variety of linked interactive plot types, providing users with the flexibility to visualize their data from multiple perspectives. The ability to navigate through various projections of the displayed tours directly within a graphical user interface (GUI) enables users to explore different aspects of the dataset. Furthermore, users can initiate new tours directly from the interface. The GUI also supports interactive feature selection, allowing users to specify which subset of features should be visualized in the plots. Once users have identified interesting views or settings, \texttt{lionfish} allows them to save the displayed projections, subsets, and plots. This functionality ensures that analysis states can be preserved for further examination or reporting, making the package particularly useful for iterative analysis where findings may need to be revisited or shared with collaborators.

@@

The \texttt{Save projections and subsets} button can be used to save the current state of the analysis. These states can be recovered by using pressing the \texttt{Load projections and subsets} button. Additionally, users can initiate new tours of various directly from the sidebar.

@@

@@

where $c_{ij}, i=1, ..., k$ (number of clusters); $j=1, ..., p$ (number of features) are a summary of each feature in each cluster. Because our examples use binary features,  the $c_{ij}$ is the number of 1's of feature $j$ in cluster $i$. %For this setting we have developed a heatmap display that we have found to be particularly useful in feature selection. The idea is to understand differences in the binary ratings between clusters, where we use different normalizations to better explore the data. For \(c_{ij}\) the count (number of true values in the binary feature) in the \(i\)-th cluster and \(j\)-th feature, we define
There are several ways that these values can be normalized to examine different aspects: $f_{ij}^{o} = \frac{c_{ij}}{n}$, $f_{ij}^{c} = \frac{c_{ij}}{n_{i}}$ and $f_{ij}^{f} = \frac{c_{ij}}{n_{j}}$, where $n_i, n_j$ are the row and column totals. The first, $f^{o}$ is the overall fraction, where counts are normalised by the overall number of observations $n$. Is generally less useful.

The second, $f^c$ is normalized relative to the size of each cluster and can be considered the distribution of features in each cluster. It is useful for comparing the composition of each cluster relative to the features. For example, for $p=4$, if $f^c_{1j} = (0.4, 0.4, 0.1, 0.1)$ it suggests that high values (1's) of features 1 and 2 distinguish cluster 1. In the context of the later examples, this would mean cluster 1 contains tourists that list engaging in activities 1 and 2 but not 3 and 4. This normalisation produces what is called the {\bf intra-cluster fraction}.

The last, $f_f$ is normalized relative to each feature, which can be considered to be the distribution of clusters on each feature. It is useful to examine how features are related to a cluster. Considering the last metric, for example, if $f^f_{i1} = (0.5, 0.4, 0, 0.1, 0)$ ($k=5$) would indicate that high values on feature 1 primarily are in clusters 1, 2. In the context of the later examples, this would mean activity 1 is commonly listed only in clusters 1 and 2. This normalisation produces what is called the {\bf intra-feature fraction}.

@@

A similar approach can be used to refine a partitioning solution. This is in particular useful to integrate prior knowledge or business interests in a given cluster solution. In the interface we can keep the provided clustering, but separate out new subsets via manual selection, for example after we found a group of particular interest via a manual tour.

>>>>

\begin{enumerate}
\item Visualizing the partitions between clusters in combinations of features using tour methods, with both a grand tour and manual tour.
\item Interactively brushing groups of points to refine the cluster solution, like done with spin-and-brush tools~\citep{ggobi}.
\item Linking multiple displays to focus on particular clusters, and simplify the problem to better understand the clustering solution. 
\item Update displays based on user selections such as feature selection or cluster selection, or re-scaling.
\end{enumerate}

@@

The interface was implemented in the R package \texttt{lionfish} and offers a variety of linked interactive plot types, providing users with the flexibility to visualize their data from multiple perspectives. The ability to navigate through various projections of the displayed tours directly within a graphical user interface (GUI) enables users to explore different aspects of the dataset. Furthermore, users can initiate new tours directly from the interface. The GUI also supports interactive feature selection, allowing users to specify which subset of features should be visualized in the plots. Once users have identified interesting views or settings, \texttt{lionfish} allows them to save the displayed projections, subsets, and plots. This functionality ensures that analysis states can be preserved for further examination or reporting, making the package particularly useful for iterative analysis where findings may need to be revisited or shared with collaborators.

@@

The \texttt{Save projections and subsets} button can be used to save the current state of the analysis. These states can be recovered by using pressing the \texttt{Load projections and subsets} button. Additionally, users can initiate new tours directly from the sidebar. The options for new tour paths are: a local tour around the currently shown projection, a guided tour that searches for projections with maximum separation between groups \textcolor{red}{XXX is this true? other options?}

\textcolor{red}{Mention additional interactive features in the displays - manual tour, anything else that might be relevant?}

@@

\textcolor{red}{Maybe here you can say something about adding new display types, what would be needed for implementing them}

@@

where $c_{ij}, i=1, ..., k$ (number of clusters); $j=1, ..., p$ (number of features) are a summary of each feature in each cluster. Because our examples use binary features,  the $c_{ij}$ is the number of 1's of feature $j$ in cluster $i$. %For this setting we have developed a heatmap display that we have found to be particularly useful in feature selection. The idea is to understand differences in the binary ratings between clusters, where we use different normalizations to better explore the data. For \(c_{ij}\) the count (number of true values in the binary feature) in the \(i\)-th cluster and \(j\)-th feature, we define
There are several ways that these values can be normalized to examine different aspects: $f_{ij}^{o} = \frac{c_{ij}}{n}$, $f_{ij}^{c} = \frac{c_{ij}}{n_{i}}$ and $f_{ij}^{f} = \frac{c_{ij}}{n_{j}}$, where $n_i, n_j$ are the row and column totals. The first, $f^{o}$ is the overall fraction, where counts are normalised by the overall number of observations $n$. This can only give an overview and is generally less useful for feature selection.

The second, $f^c$ is normalized relative to the size of each cluster and can be considered the distribution of features in each cluster. It is useful for comparing the composition of each cluster relative to the features. For example, for $p=4$, if $f^c_{1j} = (0.4, 0.4, 0.1, 0.1)$ it suggests that high values (1's) of features 1 and 2 distinguish cluster 1. In the context of the later examples, this would mean cluster 1 contains tourists that list engaging in activities 1 and 2 but not 3 and 4. This normalisation produces what is called the {\bf intra-cluster fraction}. \textcolor{red}{It corresponds to the cluster means. XXX why not larger values in the example, the maximum would be 1 so 0.4 still seems very moderate.}

The last, $f^f$ is normalized relative to each feature, which can be considered to be the distribution of clusters on each feature. It is useful to examine how features are related to a cluster. Considering the last metric, for example, if $f^f_{i1} = (0.5, 0.4, 0, 0.1, 0)$ ($k=5$) would indicate that high values on feature 1 primarily are in clusters 1, 2. In the context of the later examples, this would mean activity 1 is commonly listed only in clusters 1 and 2. This normalisation produces what is called the {\bf intra-feature fraction}. \textcolor{red}{Note that this must be interpreted with care in case of inbalanced cluster sizes.}

@@

A similar approach can be used to refine a partitioning solution. In a \textit{visual analytics} approach we use interactive visualizations to integrate human judgement with statistical and machine learning models~\citep{keim2010mastering} to optimize knowledge extraction from data.
Here this is in particular useful to integrate prior knowledge or business interests in a given cluster solution. In the interface we can keep the provided clustering, but separate out new subsets via manual selection, for example after we found a group of particular interest via a manual tour.
